\documentclass[margin]{res}  

\usepackage{helvet}

\textheight=700pt

\begin{document}

\name{Harry Potter}

\address{harryjpotter@ministryofmagic.co.uk \\(+44) 7481324987\\}

\begin{resume}

\section{OBJECTIVE}
{\sl Hogwarts dropout and recipient of 7 O.W.L.s. Specializations include Defense Against the Dark Arts, Transfiguration, and Charms. Excellent Seeker for Gryffindor Quidditch Team. }

\section{EDUCATION}
\textbf{Hogwarts School of Witchcraft and Wizardry}, Scottish Highlands\\
{\sl Bachelor of Magic}, Transfiguration, Defense Against the Dark Arts, Potions\\
September 1990 - May 1996
\hfill 7 O.W.L.s

\textbf{St. Grogory's Primary School}, Little Whinging, Surrey \\
{\sl Graduate}, \\
September 1985 - May 1990
\hfill GPA: 3.1

\section{MAGICAL\\SKILLS}

\textbf{Languages : } English, Parseltongue
\\
\textbf{Potions :} Polyjuice, Felix Felicis
\\
\textbf{Wand : } 11" Holly, Phoenix feather
\\
\textbf{Spells : } Accio, Expelliarmus, Protego
\\
\textbf{Interesting Possessions : } Invisibility Cloak, Firebolt

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{Hallows and Horcrux Hunter \hfill{Aug 97 - May 98}\\}
\normalfont{Set out to find the Deathly Hallows and hunt down Voldemort's Horcruxes.}

\section{PROJECTS}
\location{The Forbidden Forest}
\title{\textbf{Finding the Resurrection Stone \hfill May 1997}
 }
\begin{position}
% \begin{itemize}
Searched for the Resurrection Stone for a couple of months, only to realize it had been in my pocket for about nine months.
% \end{itemize}
\begin{itemize}
\item \textbf{Spells/Skills Used :} Riddle-solving
\end{itemize}
\begin{itemize}
\item \textbf{Reference :} J.K. Rowling
\end{itemize}
\end{position}

\location{The Room of Requirement}
\title{\textbf{Finding the Lost Diadem of Ravenclaw \hfill May 1997}
 }
\begin{position}
% \begin{itemize}
Worked in a 3-person team to find the Lost Diadem of Ravenclaw, which had been missing for centuries. Conveniently happened to find that the diadem's creator's dead daughter had returned to Hogwarts as a ghost, so I emotionally manipulated them into telling me where it is. To be fair, I still had to figure out her riddle, which conveniently enough referred to a room that I had stumbled across two years ago to hide my other numerous misdeeds as a student.
% \end{itemize}
\begin{itemize}
\item \textbf{Spells/Skils Used :} Accio, Flying, More riddle-solving, Stabbing with a conveniently obtained Basilisk fang
\end{itemize}
\begin{itemize}
\item \textbf{Reference :} Draco Malfoy, Hermione Granger, Roonil Wazlib
\end{itemize}
\end{position}


\section{AWARDS}
\normalfont{\textbullet{} \textbf{Quidditch House Cup} with \sl{Gryffindor House} \\ Beat Ravenclaw!}
\\
\textbullet{} \textbf{Sword of Gryffindor} in the Chamber of Secrets by \sl{Fawkes the Phoenix} \\ Used the Sword of Gryffindor to kill a basilisk that Hermione had said existed


\section{RELEVANT\\COURSES}
\par

\normalfont{\textbullet{} N.E.W.T. Potions }
\normalfont{\textbullet{} N.E.W.T. Defense Against the Dark Arts \\}
\normalfont{\textbullet{} N.E.W.T. Transfiguration}
\normalfont{\textbullet{} N.E.W.T. Charms }
\normalfont{\textbullet{} Apparition Certificate\\}
\normalfont{\textbullet{} N.E.W.T. Herbology}
\normalfont{\textbullet{} N.E.W.T. Astronomy}

\section{EXTRA-\\CURRICULARS}
\par

\normalfont{\textbullet{} Gryffindor Quidditch Team }
\normalfont{\textbullet{} Duelling Club }
\normalfont{\textbullet{} Dumbledore's Army}

\end{resume}
\(\)\end{document}